Reliable Inferences from Simply Parameterised Models

### 2013-04-06 ms.tex
Random attempts

\section{More Objective Temperature Selection}
Suppose the complex model has parameters $\eta$.
The joint prior between the simple model parameters $\theta$ and the data $D$
is given by:
\begin{eqnarray}
q_0(\theta, D).
\end{eqnarray}
We wish to approximate this by another distribution:
\begin{eqnarray}
p_T(\theta, D) &=& p(\theta)\mathcal{L}(\theta; D).
\end{eqnarray}
This approximation will be done by maximising:
\begin{eqnarray}
H(T) &=& -\int p_T(\theta, D) \log q_0(\theta, D) \, d\theta \, dD
\end{eqnarray}

>>>>

\section{More Objective Temperature Selection}
Suppose the complex model has parameters $\xi$ and the simple model
has parameters $\theta$. What we really want is the posterior for $\theta$:
\begin{eqnarray}
p(\theta|x) \propto p(\theta)p(x|\theta)
\end{eqnarray}
But the likelihood $p(x|\theta)$ is unavailable. All we have access to is the
likelihood given {\it complex} model parameters, that is, we can evaluate
$p(x|\xi)$. For the purposes of predicting data, $\xi$ makes $\theta$
redundant:
\begin{eqnarray}
p(x|\xi) = p(x|\xi, \theta)
\end{eqnarray}

Suppose we can also sample the joint distribution between $\xi$, $\theta$
and $x$.
\begin{eqnarray}
p(\xi)p(\theta|\xi)p(x|\theta, \xi) &=& p(\xi)\delta\left(
\theta - f(\xi)\right)p(x|\xi)
\end{eqnarray}
This implies the following joint distribution for $\theta$ and $x$:
\begin{eqnarray}
p(\theta, x) &=& \int p(\xi)\delta\left(
\theta - f(\xi)\right)p(x|\xi) \, d\xi
\end{eqnarray}

We shall approximate our target posterior with things we can actually
implement, and then optimise our approximation. Adding subscripts to the target
posterior:
\begin{eqnarray}
p_0(\theta|x) \propto p_0(\theta)p_0(x|\theta).
\end{eqnarray}

%The joint prior between the simple model parameters $\theta$ and the data $x$
%is given by:
%\begin{eqnarray}
%p_0(\theta, x) &=& \int p_0(\xi, \theta, x) \, d\xi \\
%&=& \int p_0(\xi)p_0(\theta|\xi)p_0(x|\theta, \xi) \, d\xi \\
%&=& \int p_0(\xi)\delta\left(\theta - f(\xi)\right)p_0(x|\theta, \xi) \, d\xi \\
%&=& \int p_0(\xi)\delta\left(\theta - f(\xi)\right)p_0(x|\theta, \xi) \, d\xi
%\end{eqnarray}
%We wish to approximate this by another distribution:
%\begin{eqnarray}
%p_T(\theta, D) &=& p(\theta)\mathcal{L}(\theta; D).
%\end{eqnarray}
%This approximation will be done by maximising:
%\begin{eqnarray}
%H(T) &=& -\int p_T(\theta, D) \log q_0(\theta, D) \, d\theta \, dD
%\end{eqnarray}
